Asteroid project summary

### 2021-11-11 summaries/hamiltonian/21-11.tex
Moved hamiltonian summary

\subsection{Hamiltonian and Equations of motion}
As a simplifying assumption, we will not model the effect of the central body's non-sphericity on the asteroid orbit. This effect has been studied in much detail and is small. We therefore separate the position dynamical variables from the angular variables and derive the standard equations of motion for asteroid position:
\begin{equation}
\dot{\bm{v}} = -\frac{GM}{r^3}\bm{r}\qquad \dot{\bm{r}} = \bm{v}.
\end{equation}
The position variables will no longer be discussed.

@@

\subsection{Initial values}
To solve for $\bm q$, $\bm p$ as functions of time, we need their values at some point in time. We study their values far from the central body before the flyby, when they are assumed to be in steady state. Here, the spin axis $\bm \omega$ is parallel to the body-fixed unit axis $\unit z$. This fixes $\beta$ and $\gamma$ while $\alpha$ is left free, expressing the initial orientation of the asteroid.

@@

>>>>

\subsection{Hamiltonian and Equations of motion}
As a simplifying assumption, we will not model the effect of the central body's non-sphericity on the asteroid orbit. This effect has been studied in much detail and is small. We therefore separate the position dynamical variables from the angular variables and derive the standard equations of motion for asteroid position:
\begin{equation}
\dot{\bm{v}} = -\frac{G\mu_M}{r^3}\bm{r}\qquad \dot{\bm{r}} = \bm{v}.
\label{eqn:translaton-eom}
\end{equation}
The position variables will no longer be discussed.

@@

\subsection{Initial values}
To solve for $\bm q$, $\bm p$ as functions of time, we need their values at some point in time. We study their values far from the central body before the flyby, when they are assumed to be in steady state. Here, the spin axis $\bm \omega$ is parallel to the body-fixed unit axis $\unit z$. This fixes $\beta$ and $\gamma$ while $\alpha$ is left free, expressing the initial orientation of the asteroid. Specifically, $\cos\beta = \omega_Z / \omega$ and $\tan\gamma = \omega_Y/\omega_X$.

@@

The orbital parameters we use to describe the orbit are the hyperbolic excess velocity $v_\infty$ and the pericenter altitude $r_p$. The orbit orientation is fixed to lie in the $\unit X-\unit Y$ plane, with pericenter lying on $\hat X$. The position of the satellite as a function of time is therefore generated by numerically integrating the Newtonian equation of motion (equation \ref{eqn:translaton-eom}) from initial values $\bm r(t=0) = r_p \unit X$ and $\bm v(t=0)=\unit Y \sqrt{v_\infty^2 + 2G\mu_M / r_p}$
